---
title: "Bootstrapping"
author: "Olya Besedina"
data: "11/14/2019"
output: github_document
---
  
```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

knitr::opts_chunk$set(
 	echo = TRUE,
 	warning = FALSE,
 	fig.width = 8, 
   fig.height = 6,
   out.width = "90%"
 )

options(
   ggplot2.continuous.colour = "viridis",
   ggplot2.continuous.fill = "viridis"
 )

 scale_colour_discrete = scale_colour_viridis_d
 scale_fill_discrete = scale_fill_viridis_d

 theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
``` 

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```

Fit two models

```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```

```{r}
sim_df_nonconst %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```

error distribution is different between the sets, but var is the same. 

# How can I bootstrap

write a function to draw a bootstrap sample based on a dataframe
size = 1 , size what you are taking, 1 is 100%

```{r}
# w/o replacement
sim_df_nonconst %>% 
  sample_frac(size = 1, replace = FALSE) %>% 
  arrange(x)

# w replacement
sim_df_nonconst %>% 
  sample_frac(size = 1, replace = TRUE) %>% 
  arrange(x)


boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

```{r}
boot_sample(df = sim_df_nonconst) %>% 
  ggplot(aes(x = x, y= y))+
  geom_point(alpha = .5)+ 
  stat_smooth(method = "lm")
  
```

Can i create a df, to keet track of boot strap sample?

Orginize a dataframe..
rerun boot_sample(sim_df_nonconst) a 1000 times

sample with replacement - gives you a diff sample of 250 people from the same sample, because some of the people will be picked more than once.

```{r}
boot_straps = 
  tibble(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )

boot_straps
```

Do some kind of analysis

What is the distribution of the slope

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(.x = strap_sample, ~lm(y ~x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(- strap_sample, - models) %>% 
  unnest(results)
```

summarize these results 

```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))
```


# Try modelr package

```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000)

sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```


# what if your assumptions are not wrong?

```{r}
sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

Good for data that does not meet the assumptions. 



# airbnb data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```


```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point()
```

error are not constant. regression assumptions are not valid. what is distribution of the slope?

Reuse the stuff I just did

```{r}
airbnb_results = 
  nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(price ~ stars, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()

```

Distribution is skewed. does not ~N distribution. 
95% CI will be your data with out 2.5% from bottom and top
















