---
title: "Linear Models"
author: "Olya Besedina"
data: "11/07/2019"
output: github_document
---
  
```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
 	echo = TRUE,
 	warning = FALSE,
 	fig.width = 8, 
   fig.height = 6,
   out.width = "90%"
 )

options(
   ggplot2.continuous.colour = "viridis",
   ggplot2.continuous.fill = "viridis"
 )

 scale_colour_discrete = scale_colour_viridis_d
 scale_fill_discrete = scale_fill_viridis_d

 theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


# linear models 

```{r}

set.seed(1)

data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

An good place to start is to consider price as an outcome that may depend on rating and borough. We fit that initial model in the following code.

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```


I cat predictors (boro), r assumes that it is a factor abd will orginize them is some order. If order is not specified than R wil use alphabetical order - Bronx

```{r,eval= FALSE}
# not very descriptive
fit

# better summary
summary(fit)

# extract the coef
coef(fit)
summary(fit)$coef

# broom::tidy gives you the same thing but orginized in nice tibble

# broom::glance gives you other important info like AIC and BIC
fit %>% 
  broom::glance()

fit %>% 
  broom::tidy()
```

Tidy the results

```{r}
fit %>% 
  broom::tidy() %>% 
  #replave default boro with nice looking one
  mutate(
    term = str_replace(term, "boro", "Boro: ")
  ) %>%
  knitr::kable(digits = 3)
```

#Take a look at factors

fct_infreq - put cat var in order of how often they occur in data set
the most freq boro is manhattan 

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```

Refit the last model 

```{r}
# now ref is manhattan
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()

```












